Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-05-01 ms.tex
minor improvements in language.

The minimum heating rate for thermal stability corresponds to {\it
  maximum} thermally-stable accretion rate. Due to the large scatter
in galaxy structural parameters at a given $\Mbh$, we use
equation~\eqref{eq:cooling3} instead of equation~\eqref{eq:cooling4}:
the $\zeta_c$ criterion should be evaluated on a galaxy-by-galaxy
basis. Thus, the maximum thermally stable $\Mdot$ (for
$\zeta>\zeta_c$) is

@@

  \item In the vicinity of the stagnation radius including the effects
    of heat transport by electron conduction results in at most order
    unity changes to the key properties of the flow (e.g. stagnation
    radius, mass accretion rate, and thermal stability) for causal
    values of the conduction saturation parameter $\phi < 0.1$
    (eq.~[\ref{eq:conduction}]). However, in principle heat conduction
    of heat from the very inner accretion flow can affect the flow on
    much larger scales \citep{Johnson+2007}. Angular momentum is also
    unlikely to invalidate our spherically symmetric model on large
    scales, given observationally inferred rotation rates of galactic
    nuclei near the stagnation radius ($\S\ref{sec:rotation}$).

>>>>

The minimum heating rate for thermal stability corresponds to {\it
  maximum} thermally-stable accretion rate. Due to the large scatter
in galaxy structural parameters at a given $\Mbh$, we use
equation~\eqref{eq:cooling3} instead of equation~\eqref{eq:cooling4}
to calculate the minimum heating rate: the $\zeta_c$ criterion should
be evaluated on a galaxy-by-galaxy basis. Thus, the maximum thermally
stable $\Mdot$ (for $\zeta>\zeta_c$) is

@@

  \item In the vicinity of the stagnation radius including the effects
    of heat transport by electron conduction results in at most order
    unity changes to the key properties of the flow (e.g. stagnation
    radius, mass accretion rate, and thermal stability) for causal
    values of the conduction saturation parameter $\phi < 0.1$
    (eq.~[\ref{eq:conduction}]). However, in principle heat conduction
    of heat from the very inner accretion flow can affect the solution
    properties on much larger scales \citep{Johnson+2007}. Angular
    momentum is also unlikely to invalidate our spherically symmetric
    model on large scales, given observationally inferred rotation
    rates of galactic nuclei near the stagnation radius
    ($\S\ref{sec:rotation}$).
